%-------------------------
% Resume in Latex
% Author : Mohamed Izhar
% Based off of: https://github.com/sb2nov/resume
% License : MIT
% Edited on: https://texviewer.herokuapp.com/
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Mohamed Izhar} \\ \vspace{1pt}
    \small +91 9022395379 $|$ \href{mailto:mohamed@izhar.xyz}{\underline{mohamed@izhar.xyz}} $|$ 
    \href{https://www.linkedin.com/in/mohamed-izhar-670128227}{\underline{in/mohamed-izhar-670128227}} $|$
    \href{https://github.com/0neTrueG0D}{\underline{github/0neTrueG0D}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ajeenkya DY Patil University}{Pune, India}
      {Bachelor of Technology in Mobile Application and Information Security}{2021 -- 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {PHP Web Developer}{Oct. 2020 -- Dec. 2022}
      {Shri Jagan Associates}{Remote}
      \resumeItemListStart
        \resumeItem{Collaborate within an Agile team structure where they will assist with developing code using such technologies as: PHP, HTML, CSS and JavaScript.}
        \resumeItem{Developed front-end web application using HTML/CSS and JavaScript.}
        \resumeItem{Worked with web debugging tools like Firefox or Chrome Developer Console}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    % need to add more expericence here

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://poeticcode.xyz}{\textbf{Poeticcode.xyz}} $|$ \emph{Python, Django, Tailwindcss, PostgreSQL, Git}}{March 2023 -- Sep. 2023}
          \resumeItemListStart
            \resumeItem{Developed a fully featured blog website using Django, Tailwind CSS, and HTMX to share coding insights and experiences.}
            \resumeItem{Implemented GitHub and Google OAuth to authenticate users and allow them to comment on posts.}
            \resumeItem{Enabled user registration, responsive UI with Tailwind CSS, dynamic content loading with HTMX, and interactive comment system.}
            \resumeItem{Used Celery and Redis for asynchronous tasks}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://pingofdeath.tech}{\textbf{Pingofdeath.tech}} $|$ \emph{Python, Django, Django Rest Framework, PostgreSQL, Git}}{Dec. 2021 -- Feb. 2023}
          \resumeItemListStart
            \resumeItem{Designed and developed a robust CRUD API for a blog using Django Rest Framework.}
            \resumeItem{Implemented JWT authentication and authorization features to ensure data security.}
            \resumeItem{Deployed the API on Vercel, optimizing for high availability and scalability.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://blogrs.shuttleapp.rs/}{\textbf{Blogrs}} $|$ \emph{Rust, Axum, PostgreSQL, Shuttlers, Git}}{Dec. 2021 -- Feb. 2023}
          \resumeItemListStart
            \resumeItem{Developed and implemented "blogrs," a Rust-based API using Axum framework.}
            \resumeItem{Utilized PostgreSQL as the database backend to ensure efficient data storage and retrieval.}
            \resumeItem{Leveraged Rust programming language and Axum framework to build a high-performance and lightweight API.}
            \resumeItem{Successfully deployed the project on shuttleapp.rs, showcasing proficiency in deployment and server management.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Neoplayer} $|$ \emph{TypeScript, React, React Native, Redux, Git}}{Oct. 2023 -- Dec. 2023}
          \resumeItemListStart
            \resumeItem{Designed and developed a sleek and intuitive music player app using React Native.}
            \resumeItem{Implemented a Neumorphic user interface for a modern and visually appealing design.}
            \resumeItem{Features include music playback controls, playlist management, and a user-friendly interface.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Rust, C, Kotlin, JavaScript, Python, Bash, SQL (Postgres), HTML/CSS} \\
     \textbf{Frameworks}{: Django, Svelte, ReactNative, React, Nextjs, Node.js, Tauri, Tailwindcss} \\
     \textbf{Developer Tools}{: Linux, Git, Docker, Vercel, VS Code, Vim, Android Studio, QEMU/KVM} \\
     \textbf{Libraries}{: Threejs, GSAP, Django Rest Framework} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}